### 2014-11-01 evaluation.tex
Committing first experiments

We deploy \name applications in \emph{clusters} where each cluster is composed
of 5 fully replicated Cassandra replicas within the same datacenter. We
instantiate one shim layer node for every cassandra replica, an place it on the
same VM as the cassandra replica. The clients are instantiated on the same data
center as the store.

>>>>

We deploy \name applications in \emph{clusters} where each cluster is composed
of 5 fully replicated Cassandra replicas within the same datacenter. We
instantiate one shim layer node for every cassandra replica, an place it on the
same VM as the cassandra replica. The clients are instantiated on the same data
center as the store, and run the transactions. We deploy the each node in the
cluster cluster on \cf{c3.4xlarge} Amazon EC2 instances with 16 virtual CPUs,
30GB memory, and 320GB of SSD storage. Our shim layer nodes are multi-threaded,
and we allocate 8 CPUs for each shim layer node. The clients also run on
\cf{c2.4xlarge} instances. We call this deployment \cf{1DC}. For our WAN
experiments, we instantiate 2 clusters (each with 5 nodes), one in US-east (N.
Virginia) and another in US-west (Oregon). The average latency between the
regions was 85 ms. We call this deployment \cf{2DC}.

\subsection{LWW Register}

\begin{figure*}
  \centering
  \subfigure[Perf. Oper. 1DC]{\label{grf:LWW-perf-1DC}\includegraphics[width=0.24\textwidth]{graphs/LWW-tp-vs-lat-1DC.pdf}}
  \subfigure[Perf. Oper. 2DC]{\label{grf:LWW-perf-2DC}\includegraphics[width=0.24\textwidth]{graphs/LWW-tp-vs-lat-2DC.pdf}}
  \subfigure[Perf. Txn. 1DC]{\label{grf:LWW-txn-1DC}\includegraphics[width=0.24\textwidth]{graphs/LWW-tp-vs-lat-1DC-txn.pdf}}
  \subfigure[Mutation Prof. 1DC]{\label{grf:LWW-txn-wp}\includegraphics[width=0.24\textwidth]{graphs/LWW-txn-wp-vs-tp.pdf}}
	\caption{Performance of LWW Register RDT.}
  \label{grf:LWW_perf}
\end{figure*}

We analyze the performance of different consistency classifications in \name
using the LWW register. Our client workload was generated using YCSB
benchmark~\cite{}, with the default workload of 50\% reads and 50\% writes,
with keys uniformly chosen from a set of 1000 keys. We varied the number of
clients from 128 to 1024, with each workload running for 180 seconds.
Last-writer-wins is the conflict resolution policy used by Cassandra. Hence, we
are able to directly compare the performance of \name implementation against
Cassandra.

Figure~\ref{grf:LWW-perf-1DC} shows the throughput vs. latency graph for the
different consistency levels. We also include Cassandra, which provides basic
eventual consistency. Recall that \name's eventual consistency is stronger than
the guarantees provided by Cassandra (Section~\ref{sec:store_sem}). With 512
clients, the average latency of operations on Cassandra was 32.24 milliseconds.
EC and CC under \name was 30\% and 57\% slower whereas strong consistency was
241\% slower. EC(SC) was able to achieve 80\%(40\%) of throughput of vanilla
Cassandra. The results show that while \name provides an expressive programming
model with stronger consistency guarantees, its performance is comparable to
vanilla Cassandra. However, SC has a huge performance hit due to coordination
between all the replicas for obtaining object leases as well as reading and
writing to all replicas.
